Profile likelihoods for geostatsistical models using GPU's

### 2022-01-08 pkg/oldgpuRandom/inst/doc/L2021_11/paper2.tex
paper 2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3097 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
paper2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3103 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{CI’s comparison for model parameters}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
R> library(gpuRandom)
R> library(gpuR)
R> library(data.table)
R> # library(geostatsp)
\end{verbatim}
\end{kframe}
\end{knitrout}

% swissrain matplot over betas

%meuse data

@@

>>>>

\subsection{swissRain example}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{table}[H]

\caption{\label{tab:swisssummarycompare}Summary comparison}
\centering
\begin{tabular}[t]{rcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{geostatsp} & \multicolumn{2}{c}{gpuBatchMatrix} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Parameter & Estimate & 95\% CI & Estimate & 95\% CI\\
\midrule
range & 38618.730 & (21805.93, 68394.54) & 38618.730 & NA\\
sdNugget & 0.992 & (0.684,1.439) & 0.992 & NA\\
shape & 1.826 & (-0.574,4.227) & 1.826 & NA\\
anisoRatio & 8.092 & (5.321,12.305) & 8.092 & NA\\
anisoAngleRadians & 0.652 & (0.595, 0.709) & 0.652 & NA\\
boxcox & 0.496 & (0.373,0.620) & 0.496 & NA\\
\bottomrule
\end{tabular}
\end{table}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}[H]

{\centering \includegraphics[width=0.5\linewidth]{profile_logl_swiss}

}

\caption[profile LogL of slope parameter]{profile LogL of slope parameter}\label{fig:swiss_profile_many}
\end{figure}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}

{\centering \includegraphics[width=1\linewidth]{swiss_pro_4}

}

\end{knitrout}

\subsection{meuse example}

@@

Estimates by \pkg{geostatsp}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
##                    estimate   ci0.005 ci0.995
## (Intercept)         0.91634  0.121205   1.711
## sqrtdist           -0.08445 -1.623508   1.455
## sdNugget            0.00785  0.000379   0.163
## sdSpatial           0.01250  0.000690   0.227
## range             173.16439 92.775636 323.209
## shape               4.00000 -9.880685  17.881
## anisoRatio          2.30106  1.138810   4.649
## anisoAngleRadians   0.27490 -0.167582   0.717
## anisoAngleDegrees  15.75042 -9.601751  41.103
## boxcox             -0.90390 -2.558961   0.751
## m2logL.ml   logL.ml 
##     133.4     -66.7
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
R> result3 <- gpuRandom::likfitLgmCov(spatialmodel = Res1, params = params,
+      boxcox = c(1, 0, -0.903901505), paramToEstimate = c("range", "shape",
+          "nugget", "sdNugget", "anisoRatio", "anisoAngleRadians"), cilevel = 0.95,
+      type = "double", reml = FALSE, NparamPerIter = 400, Nglobal = c(128,
+          64), Nlocal = c(16, 16), NlocalCache = 2800, verbose = FALSE)
## workgroupSize
## 128 64
## localSize
## 16 16
## 
##  Nparams 50176 NparamsPerIter 400 Niter 126 Ncovariates 2 Ndatasets 3 NlocalCacheD 1272
\end{verbatim}
\end{kframe}

{\centering \includegraphics[width=\maxwidth]{figure/meuse_logl-1}

}

\begin{kframe}\begin{verbatim}
R> result3$summary
##                   estimate lower95ci upper95ci
## (Intercept)         0.9162        NA        NA
## sqrtdist           -0.0843        NA        NA
## sdSpatial           0.0126        NA        NA
## range             173.1644   100.000  277.7688
## shape               6.0000     0.784    6.0000
## nugget              0.3947     0.000    1.1582
## sdNugget            0.0079     0.000    0.0135
## anisoRatio          2.3011     1.469    5.5220
## anisoAngleRadians   0.2749     0.000    0.5604
## boxcox             -0.9039        NA        NA
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
R> count/Nsim
## [1] 0.81
R> mean_estimates
## (Intercept)        cov1        cov2   sdSpatial       range 
##       2.992       1.000       0.500       0.492     986.372 
##      nugget 
##       4.427
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{p2Rplot_100} 
\includegraphics[width=0.5\linewidth]{rsplot}

}

\caption[range and nugget contours]{range and nugget contours}\label{fig:showgraphs}
\end{figure}

\end{knitrout}
